---
title: "traktok - Methods Hub"
format:
  html:
    embed-resources: true
  gfm: default
---

# traktok: Access TikTok Data from R

## Description

`traktok` is an R package for collecting **TikTok** data. It supports the official **TikTok Research API** (for eligible researchers) and a browser-mimicking **hidden API** (unofficial) to retrieve videos, users, comments, and relationships for research use. Outputs are tidy tibbles suitable for downstream analysis and archiving.

> **Stability note:** Hidden/unofficial endpoints can break without notice if TikTok changes request formats or storage. The package is maintained actively, but functions may require updates over time.

## Use Cases

- **Collect platform samples** for for example by hashtags or keywords, to study mobilization, misinformation or topic visibility.
- **Retrieve engagement signals** (like, share, comments, play counts) to model content diffusion and attention.
- **Map network relations** (followers/following) for influence analyses.
- **Download media** (video files) for computational content analysis (e.g., frames, audio, OCR)-subject to legal/ethical review.
- **Combine Research API and hidden API** to cover gaps in coverage.

## Input Data

- **No local input required** to start: you provide search terms or identifiers (e.g., hashtags, user names, video URLs or IDs), and the package contacts TikTok’s services and returns the results as tibbles (data frames).
- **Authentication:** Some endpoints require authentication - via `auth_research()` (Research API) or `auth_hidden()` (hidden API). See the package vignettes or below for information about the setup.
- **What you provide:** Depending on the function, you specify hashtags/keywords, user handles/IDs, video URLs/IDs, or playlist IDs.

## Output Data

Most functions return **tibbles** with columns like:

- General:`video_id`, `video_url`, `video_timestamp`, `video_length`, `video_title`  
- Engagement: `video_diggcount`, `video_sharecount`, `video_commentcount`, `video_playcount`, `video_is_ad`  
- Author/user: `author_name`, `author_username`, `author_nickname`, `author_followercount`, `author_followingcount`, `author_heartcount`, `author_videocount`, `author_diggcount`  
- Nested: `music`, `challenges`, and for downloads `download_url`, `video_fn`   

Exact fields vary by endpoint; see function docs and vignettes.

```{r}
# Example: minimal toy output structure
example_output <- data.frame(
  video_id           = c("123", "456"),
  video_url          = c("https://www.tiktok.com/@user1/video/123",
                         "https://www.tiktok.com/@user2/video/456"),
  video_length       = c(12L, 34L),
  video_title        = c("Example video 1", "Example video 2"),
  video_diggcount    = c(100L, 250L),
  video_commentcount = c(10L, 40L)
)

str(example_output)
```

## Hardware Requirements
Typical API sampling is lightweight (CPU/RAM) and will run on any machine, that can run R. Media downloads may require disk space and bandwidth (e.g., gigabytes for many videos).

## Environment Setup
Make sure that you are using the most recent package versions to ensure functionality. If you encounter any issues take advantage of the Issue Tracker, which you can find under "Contact Details".
```{r, warning=FALSE, message=FALSE}
library("chromote")
library("traktok")
library("cookiemonster")
```

## How to Use

**Note:** Most of the examples below require authentication and network access and are therefore set to `eval = FALSE` by default. Execution in an interactive environment is not advised, instead we would suggest running this file on your own machine, especially when you want to use the unofficial API.

### Feature overview (selected)
The following table gives an overview of commonly used helper functions that you will use in typical workflows (searching for videos, retrieving user data, downloading media, etc.):

| Description | Shorthand | Research API | Hidden API |
|:---|:---|:---|:---|
| search videos | `tt_search` | `tt_search_api` | `tt_search_hidden` |
| get video detail (+file) | `tt_videos` | – | `tt_videos_hidden` |
| get user videos | `tt_user_videos` | `tt_user_videos_api` | `tt_user_videos_hidden` |
| get user info | `tt_user_info` | `tt_user_info_api` | `tt_user_info_hidden` |
| get comments under a video | `tt_comments` | `tt_comments_api` | – |
| who follows a user | `tt_get_follower` | `tt_user_follower_api` | `tt_get_follower_hidden` |
| who a user follows | `tt_get_following` | `tt_user_following_api` | `tt_get_following_hidden` |
| liked videos | `tt_get_liked` | `tt_user_liked_videos_api` | – |
| pinned videos | `tt_get_pinned` | `tt_user_pinned_videos_api` | – |
| playlist videos | `tt_playlist` | `tt_playlist_api` | – |
| raw post data | – | – | `tt_request_hidden` |
| authenticate | – | `auth_research` | `auth_hidden` |

### Authenticate (choose one)

In order to use the R package and access data from TikTok, authentication is
required. You can choose between the official Research API or the unofficial
hidden API.

> **Running in mybinder.org?** Neither method stores credentials between
> sessions - you will need to re-authenticate each time you launch a new
> session.

#### Option A: Research API

This requires approved access from TikTok. If you have not applied yet and for further information, see the
[Official API Guide](https://jbgruber.github.io/traktok/articles/research-api.html).

```{r, eval=FALSE}
auth_research()
```

#### Option B: Hidden API

To get started with the hidden API, see the
[Unofficial API Guide](https://jbgruber.github.io/traktok/articles/unofficial-api.html).

Authentication relies on cookies exported from your browser's TikTok session.
Follow these steps before running the code below:

1. Log into TikTok in your browser.
2. Install a cookie export extension:
   [Get cookies.txt LOCALLY](https://chromewebstore.google.com/detail/get-cookiestxt-locally/cclelndahbckbenkjhflpdbgdldlbecc)
   for Chromium-based browsers, or
   [cookies.txt](https://addons.mozilla.org/en-US/firefox/addon/cookies-txt/)
   for Firefox.
3. Export the cookies for `tiktok.com`. The file is typically named
   `www.tiktok.com_cookies.txt`.
4. **Upload the file to this session** using the file browser (RStudio:
   *Files* pane → *Upload*; Jupyter: folder icon in the left sidebar) or add them to your local working directory, when running this document locally.

Once the file is uploaded and visible in your working directory, run:

```{r, eval=FALSE}
cookiemonster::add_cookies("www.tiktok.com_cookies.txt")
auth_check()
```

> **Note:** Uploaded files are not retained between sessions. Keep your
> exported cookies file somewhere easy to find on your computer so you can
> re-upload it next time.

## Examples

The following examples use the **official Research API** only. This requires approved Research API access from TikTok (see Option A above). Using the **hidden/unofficial API** is not possible within the mybinder.org environment, and therefore there are no examples using the unofficial API listed below. If you want to access TikTok by using the unofficial API, you need to download this file, run it locally and replace the example commands below with their respective unofficial API version, which you can find in the package documentation.

### Search videos by hashtag
Use `tt_search_api()` to search TikTok by hashtag via the official Research API. In this example we are looking for videos with the #rstats hashtag. The result is a tibble with video metadata such as video IDs, author names, engagement counts, and timestamps.

```{r, eval=FALSE}
rstats_vids <- tt_search_api(
  "#rstats",
  start_date = as.Date(Sys.Date() - 30),
  end_date = Sys.Date(),
  max_pages = 2L
)

rstats_vids

# **Hidden API alternative** (for local use):
#tt_search
```

### Get comments on a video

Once you have video IDs from a search, you can retrieve all comments for a
specific video using `tt_comments_api()`. Comments are a common starting point
for text analysis, sentiment analysis, or studying audience reactions.

The function accepts either a numeric video ID or a full TikTok URL. Here we
pass the ID of the first video from the earlier search result:

```{r, eval=FALSE}
comments <- tt_comments_api(video_id = rstats_vids$video_id[1])
dplyr::glimpse(comments)
```

The returned tibble contains one row per comment and includes the fields
`text`, `like_count`, `reply_count`, `create_time`, `id`, and
`parent_comment_id` (useful for reconstructing reply threads).

> **Note:** Fetching comments counts against your daily Research API quota
> (up to 100,000 records per day). For videos with many comments, consider
> setting `max_pages` to limit the number of requests.
>
> **Hidden API:** There is no equivalent hidden API function for comments -
> `tt_comments_api()` is only available through the official Research API.

### Get user information (Research API)

To retrieve basic information about an account, use `tt_user_info_api()`. This can be useful if you want to inspect account-level metadata before deciding whether to collect additional material.

```{r, eval=FALSE}
u <- tt_user_info_api(username = "statisticsglobe")
dplyr::glimpse(u)

# **Hidden API alternative** (for local use):
#u <- tt_user_info_hidden("statisticsglobe")
```

### Download videos to a local folder

> **Hidden API only:** Downloading the actual video files is not available through the official Research API. The code below uses the hidden/unofficial API (`tt_videos()`) and requires browser cookies to be set up as described under Option B. Keep it as a local reference if you need this feature.

```{r, eval=FALSE}
# Requires hidden API authentication (Option B)
dir.create("videos", showWarnings = FALSE)

dl <- tt_videos(
  rstats_vids$video_url,
  dir = "videos",
  verbose = FALSE
)

dl

tibble::tibble(
  file = list.files("videos"),
  size_Mb = file.size(list.files("videos", full.names = TRUE)) / 1e6
)
```

## Technical Details

See the [official blogpost](https://www.johannesbgruber.eu/post/2023-12-04-re-release-traktok/) for further information about technical details.

## References

- Hohner, J., Kakavand, A., & Rothut, S. (2024). Analyzing Radical Visuals at Scale: How Far-Right Groups Mobilize on TikTok. *Journal of Digital Social Research, 6*(1), 10–30. [https://doi.org/10.33621/jdsr.v6i1.200](https://doi.org/10.33621/jdsr.v6i1.200)
- Widholm, A., Ekman, M., & Larsson, A. O. (2024). A Right-Wing Wave on TikTok? Ideological Orientations, Platform Features, and User Engagement During the Early 2022 Election Campaign in Sweden. *Social Media + Society, 10*(3). [https://doi.org/10.1177/20563051241269266](https://doi.org/10.1177/20563051241269266)
- Wirz, D. S., Zai, F., Vogler, D., Urman, A., & Eisenegger, M. (2023). *Die Qualität von Schweizer Medien auf Instagram und TikTok*. [https://doi.org/10.5167/UZH-238605](https://doi.org/10.5167/UZH-238605)
- Bach, P., Gitomer, A., Devries, M., Walker, C., Deyoe, D., Atienza-Bathelemy, J., Foucault Welles, B., Freelon, D., & Zulli, D. (2023, October). *Stitching Politics and Identity on TikTok*. Panel at AoIR2023, Philadelphia, PA.
- Giglietto, F. (2024). *Dashboard: TikTok Coordinated Sharing Network*. [https://fabiogiglietto.github.io/tiktok_csbn/tt_viz.html](https://fabiogiglietto.github.io/tiktok_csbn/tt_viz.html)

## Disclaimer

This method is for research purposes only. Use is subject to TikTok’s Terms and applicable law. Hidden API access is unofficial; functionality may break and policies can change. Handle personal data lawfully (e.g., GDPR), minimize retention, and anonymize where appropriate. Obtain any necessary ethics approvals.

## Contact Details

- **Issue-Tracker:** <https://github.com/JBGruber/traktok/issues>
- **Contact:** <JohannesB.Gruber@gmail.com>
